

\documentclass[12pt]{article}

\setlength{\oddsidemargin}{0.20truein}
\setlength{\evensidemargin}{0.20truein}
\setlength{\textwidth}{6.0truein}
\setlength{\topmargin}{0.2truein}
\setlength{\textheight}{8.0truein}

%\setlength{\oddsidemargin}{0.00truein}
%\setlength{\evensidemargin}{0.00truein}
%\setlength{\textwidth}{6.750truein}
%\setlength{\topmargin}{-0.0truein}
%\setlength{\textheight}{8.5truein}

\def\theequation{\thechapter. \arabic{section}. \arabic{equation}}

%\pagestyle{empty}

%\input newcommand

% \newcommand{\bfbeta}{\bm{\beta}}
%\usepackage{mathrsfs}

%\usepackage{bm}

%\usepackage{makeidx}

%\usepackage{multind}

%\usepackage{graphicx}


\begin{document}

\ \\
{\bf \large Corrections to second edition  \\ [.1in]
  {\em Analysis of Ordinal Categorical Data} }

\ \\ \ \\ Thanks to those who have pointed out errors, including Garry
Anderson, Veronika Ga\^sparovi\^cov\'a, David Hoaglin, Theo Nijsse,
Nigel Smeeton, and Marek Omelka.  Some of these errors have, I hope,
been corrected in later printings of the book.

\ \\
\ \\
p. 6, Figure 1.1: In the label on the vertical axis of the 
right-hand plot, the y should not have an asterisk. \\
\ \\
p. 28: In Table 2.5 and in the formula for SE, 1698 should be 1701. \\
\ \\
p. 35: The count for the (mismatch, extreme) cell should be 1, as
should the total in that column. \\
\ \\
p. 89: The sentence with the third displayed equation, namely ``The
corresponding model for the category probabilities is ...'' should
be deleted.  The correct formula for the model, which is clearer 
following the discussion in Section 4.1.3, is
%
\[
\pi_j(\mathbf{x}) = \frac{\exp(\sum_{k=j}^{c-1} \alpha_k 
+ (c-j)\bm{\beta}'\mathbf{x})}
{1 + \sum_{k=1}^{c-1} \exp(\sum_{k'=j}^{c-1}\alpha_{k'} 
+ (c-j)\bm{\beta}'\mathbf{x})}, \quad
j = 1, 2, \ldots , c-1.
\]
%
\ \\
p. 139: The intercept for the mean response model, reported as
$-5.08$, should not have the minus sign. \\
\ \\
p. 153: For the output shown in Table 6.3, the column scores
were (3, 2, 1) rather than (1, 2, 3), which is why $\hat\beta
= 0.390$ instead of $\hat\beta = - 0.390$ as stated in the text.
Likewise, on p. 154, the marginal mean reported for opinion
about astrology is based on the scores (3, 2, 1), which is why
the mean is reported as 2.63, instead of 1.37, as it would be for
the scores (1, 2, 3).  The standardized scores should then
also have reverse order and reversed sign. \\
\ \\
p. 217: According to an email I received from Veronika Ga\^sparovi\^cov\'a,
she and her thesis advisor Dr.\ J\'an Somor\^cík at Comenius University Bratislava in Slovakia believe that under the first square root in the formula for $\phi_{ij}$, $(1 - \sum_a \pi_{a+}^2)(1 - \sum_b \pi_{+b}^2)$ should be $(1 - \sum_a \pi_{a+}^2)/(1 - \sum_b \pi_{+b}^2)$, which apparently then agrees with the formula given in my 1976 article about ordinal measures of association.  I myself have not been able to check this.\\
\ \\
p. 230: In the example, the second sample mean should be 3.789
(instead of 3.799). \\
\ \\
p. 250: In the displayed formulas for popular choices for the weights
for weighted kappa, 1 should be separate rather than in the numerator
of the ratios shown; e.g., $w_{ij} = 1 - \frac{|i-j|}{c-1}$. \\
\ \\
p. 290: Ten lines from the bottom, ``estimated time at time 1''
should be ``estimated odds at time 1''. \\
\ \\
p. 332: For the ML analysis, the SE is reported as 0.395 in the text
but 0.396 in Table 11.5.  Each is actually correct, as Newton-Raphson
(observed information) yields 0.395 whereas Fisher scoring (expected
information) yields 0.396. \\

\ \\



\end{document}
